### 2016-03-13 paper/result_stereo.tex
Hang

\mysubsubsection{Stereo}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel $\alpha$-expansion method, respectively. The energy is in $\log$ scale}
  \label{fig:stereo_global}
\end{figure}

Figure \ref{fig:stereo_global} shows the

\hang{}

>>>>

\mysubsubsection{Stereo}

We performed our experiments on the half-size Book sequence from Middlebury stereo
datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy (minimum energy
so far from all threads) against time.

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{Per thread energy. The left and right figures show the
    energy minimization process on each working thread of our method
    in SF-MF configuration and parallel $\alpha$-expansion method,
    respectively. The energy is in $\log$ scale}
  \label{fig:stereo_threads}
\end{figure}

Figure \ref{fig:stereo_global} shows the energy minimization process
against time. In this experiment, both PAE and SF-MF converge faster
than sequential method. However, since fusing solutions with multiple
labels by QPBO is slower than a single $\alpha$-expansion, PAE method
reaches convergence faster than SF-MF. Architectures with multiway
fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
the TRWS algorihtm used in multiway fusion is slower than multiple
$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
jump when fusing on root node of the tree. This is because any fusion
step on non-root nodes only have partial label information.

Figure \ref{fig:stereo_threads} shows the per-thread energy
minimization process in SF-MF and PAE. The per-thread energy in SF-MF
architecture decreases more uniformly than that of PAE. In the
scenario where we need to query the best solution so far before the
whole optimization converges, SF-MF architecture is a better choice.

For a easy optimization problem as shown in this section, our full
architecture with solution sharing and multiway fusion actually makes
convergence slower by adopting sophisticated algorihtm and introducing
multi-threading overhead. However, we can easily configure the
architecture to make it better fit the problem, e.g. turn off multiway
fusion and/or solution sharing.

\hang{The end of stereo experiment......}

### 2016-03-13 paper/stereo.tex
Hang

\hang{To evaluate the effectness of different parallel structures, we
  plot the energy minimization process against time. We define the
  energy of the parallel system at a certain time as the minimum
  energy of all threads at that time.}

@@

%
We performed our experiments on Book sequence from Middlebury stereo datasets.~\cite{middlebury_stereo}.

>>>>

\hang{To evaluate the effectness of different parallel structures, we
  plot the energy minimization process against time. We define the
  energy of a parallel system at a certain time as the minimum
  energy of all threads at that time.}

@@

%
